Papers

### 2022-12-31 quarto/index.qmd
div

<img src="img/aston.jpg"  border="0" vspace="10" hspace="0" class="bio-photo"><br>
<img src="img/email.png" height="30" width="200" vspace="0" ><br>

<p align="left">
	<a href="https://twitter.com/astonzhangAZ" title="Twitter" target="_blank"><img src="./img/logo-twitter.svg" class="bio-icon"></a>
	<a href="https://github.com/astonzhang" title="GitHub" target="_blank"><img src="./img/logo-github.svg" class="bio-icon"></a>
</p>

@@

## Recent Papers

@@

## All Papers

[List](papers.qmd)

>>>>

<div class="container">

<div class="fixed"><img src="img/aston.jpg" width="200" border="0" vspace="20" hspace="0" class="bio-photo"></div>
<div class="flex-item">
<img src="img/email.png" height="30" width="200" vspace="50" ><br>
<p align="left">
	<a href="https://twitter.com/astonzhangAZ" title="Twitter" target="_blank"><img src="./img/logo-twitter.svg" class="bio-icon"></a>
	<a href="https://github.com/astonzhang" title="GitHub" target="_blank"><img src="./img/logo-github.svg" class="bio-icon"></a>
</p>
</div>

</div>

@@

## Papers ([All](papers.qmd))

@@
